\Uchapter{Preface}
The first edition of this book appeared in 1985. It described \ltx{} 2.09 , the first widely 
used version of \ltx{}. Since then, I4W has become extremely popular, with many thousands of users 
around the world. Its functionality has grown through the efforts of many people. The time has come for a new version,
\ltxee{}, which is described in this edition. Hw 2E includes many of the enhancements that were made to \ltx{} 2.09, 
as well as some new ones.



I implemented most of \ltx{} 2.09 myself. \ltxee{} was implemented by a group led by Frank Mittelbach, 
which included Johannes Braams, David Carlisle, Michael Downes, Alan Jeffrey, Chris Rowley, 
Sebastian Rahtz, and Rainer Schopf. They were assisted by many testers of the new version, and by
the following organizations: the American Mathematical Society, the Open University (UK), and the 
Zentrum fiir Datenverarbeitung der Universitat Mainz. Lyle Ramshaw helped with the implementation 
of Bezier curves. My thanks to all of these people-especially Frank and Chris, with whom I have spent many
enjoyable hours arguing about \ltx{}. 

\ltx{} has been made more useful by two programs:\hologo{BibTeX}, written by Oren Patashnik, and MakeIndex, 
written by Pehong Chen and modified by Nelson Beebe.

Many people helped me write this book-often without knowing it. Advice
given to me over the years by Cynthia Hibbard and Mary-Claire van Leunen
has found its way onto a number of these pages. Andrei Broder was my local
informant for Romanian. Helen Goldstein assisted with research on matters
ranging from art to zoology.

This edition was improved by the corrections and suggestions of Marc Brown,
Michel Goossens, and the implementers of \ltxee{}. Stephen Harrison helped
produce the final output. Errors and infelicities in the first printing were found
by Rosemary Bailey, Malcolm Clark, and Ellen Gilkerson. The following people 
found errors in, or suggested improvements to, the previous edition: Martin
Abadi, Helmer Aslaksen, Barbara Beeton, Rick Clark, John DeTreville, Mathieu 
Federspiel, Michael Fischer, Stephen Gildea, Andy Hisgen, Joseph Hurler,
Louis E. Janus, Dave Johnson, Charles Karney, Nori Kawasaki, Steve Kelem,
Mark Kent, William LeFebvre, Jerry Leichter, Hank Lewis, Stephen Peckham,
Hal Perkins, Flavio Rose, Scott Simpson, David Sullivan, Matthew Swift, Walter
Taylor, Joe Weening, Sam Whidden, Edgar Whipple, Chris Wilson, David Wise,
and Rusty Wright. I also received helpful comments and complaints about preliminary 
versions of \ltx{} and of the first edition of this book from Todd Allen, Robert Amsler, David Bacon, 
Stephen Barnard, Per Bothner, David Braunegg, Daniel Brotsky, Chuck Buckley, Pave1 Curtis, Russell Greiner, Andrew Hanson,
Michael Harrison, B. J. Herbison, Calvin W. Jackson, David Kosower, Kenneth Laws, Tim Morgan, Mark Moriconi, 
Stuart Reges, A. Wayne Slawson, David Smith, Michael Spivak, Mark Stickel, Gary Swanson, Mike Urban, Mark
Wadsworth, and Gio Wiederhold. Assistance in the development of \ltx{}2.09 was provided by 
David Fuchs, Richard Furuta, Marshall Henrichs, Lynn Ruggles, Richard Southall, Chris Torek, 
Howard Trickey, and SRI International.


Since the introduction of version 2.09, my work on \ltx{} has been supported
by Digital Equipment Corporation. I want to thank Robert Taylor and all the
other members of Digital's Systems Research Center for making it a fun place
to work.

Finally, I want to express my special thanks to two men who made this book
possible. Donald Knuth created \TeX{}, the program on which \ltx{} is based. He
also answered all my questions, even the stupid ones, and was always willing to
explain \TeX{}'s mysteries. Peter Gordon persuaded me to write the first edition,
despite my doubts that anyone would buy a book about a typesetting system.
Over the years, he has provided advice, fine dining, and friendship.


\bigskip
{\hfill L. L.}\\
{Palo Alto, California\hfill}\\
{September 199\hfill}